Storing messages with multipartite neural cliques

### 2014-07-21 Articles/article.tex
...

	\subsubsection{Simulations}
	See Figure \ref{corruptth} compares the two rules.
	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.

@@

	$\eta_\psi = max_x \, \eta_{x, \psi}$
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

>>>>

	\subsubsection{Simulations}
	See Figure \ref{corruptth} compares the two choices $w = 1$ and $w = a$.
	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.

@@

	$\eta_\psi = max_x \, \eta_{x, \psi}$
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/figpsic8l256e4psi2percent}%thpsi_c8l256e4}
		\caption{$\psi = 0.02$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}
